Classical mechanics as the high-entropy limit \\ of quantum mechanics

### 2025-12-02 Articles/2024-ClassicalLimit/classicalLimitArticle.tex
Hyphens

While we concentrated on the one dimensional case, the result can be generalized to multiple dimensions by performing a similar stretching operation on all degrees of freedom simultaneously. That is, the entropy, as it increases, it spreads equally not just within each degree of freedom, but also across degrees of freedom. This would give us $[T_Q(X^i),T_Q(P_i)] = \lambda \imath \hbar$, so that the same stretching factor is associated to all the appearances of $\hbar$ in the commutation relationship.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{stretchedCat.png}
	\caption{A cat state stretched with different values of $\lambda$. The axes are stretched by $\sqrt{\lambda}$ as well. The color scale is reduced to match the range of the function, though white always corresponds to zero. While the positive and negative peaks have comparable magnitude initially, the stretching map dampens the negative peak much more quickly. Note that, consistently with Fig. \ref{fig:uncertainty_scaled}, the negative values are severely dampened with $\lambda=5$.}
	\label{fig:cat_streatched}
\end{figure}

>>>>

While we concentrated on the one-dimensional case, the result can be generalized to multiple dimensions by performing a similar stretching operation on all degrees of freedom simultaneously. That is, the entropy, as it increases, spreads equally not just within each degree of freedom, but also across degrees of freedom. This would give us $[T_Q(X^i),T_Q(P_i)] = \lambda \imath \hbar$, so that the same stretching factor is associated to all the appearances of $\hbar$ in the commutation relationship.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{stretchedCat.png}
	\caption{A cat state stretched with different values of $\lambda$. The axes are stretched by $\sqrt{\lambda}$ as well. The color scale is reduced to match the range of the function, though white always corresponds to zero. While the positive and negative peaks have comparable magnitude initially, the stretching map dampens the negative peak much more quickly. Note that, consistently with Fig.~\ref{fig:uncertainty_scaled}, the negative values are severely dampened with $\lambda=5$.}
	\label{fig:cat_streatched}
\end{figure}
